Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-09-23 review_article.Rmd
Cartogram with single legend

load("usa_legend.rda")

@@

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(aus1), 0, .5, 0.5, 0.5) +
  draw_plot(rasterGrob(aus2), 0.5, 0.5, 0.5, 0.5) +
  draw_plot(rasterGrob(aus3), 0.0, 0.0, 0.5, 0.5) +
  draw_plot(rasterGrob(aus4), 0.5, 0, 0.5, 0.5)+
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```

>>>>

load("figures/usa_legend.rda")

@@

load("figures/aus_legend.rda")

library(cowplot)
ggdraw() +
  draw_plot(rasterGrob(aus1), 0, .5, 0.5, 0.45) +
  draw_plot(rasterGrob(aus2), 0.5, 0.5, 0.5, 0.45) +
  draw_plot(rasterGrob(aus3), 0.0, 0.0, 0.5, 0.45) +
  draw_plot(rasterGrob(aus4), 0.5, 0, 0.5, 0.45) +
  draw_plot(aus_legend, 0, 0, 1, 0.1) +
  draw_plot_label(c("a", "b", "c", "d"), 
    c(0, .5, 0, 0.5), 
    c(1, 1, .5, .5), size = 20)
```
